surfing

### 2021-05-14 inst/surfing.Rmd
typo

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table))[wanted]
names(rO) <- rownames(surfing_table)[wanted]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```

>>>>

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table[wanted,]))
names(rO) <- rownames(surfing_table)[wanted]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```
